### 2015-06-10 improv.tex
eqdef and other minor fixes

%!TEX root =  autocontgrlp.tex
\section{Improved Bounds}\label{sec:improv}
In this section, we present improved error bounds by making use of Lyapunov functions. 
\begin{lemma}\label{bestbndmn}
Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\argmin_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
\begin{align}
||J^*-\bj||_{\infty,1/\psi}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\infty,1/\psi} \psi\geq TJ^*$.
\end{proof}

Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the modified $L_\infty$ norm.

@@

The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in modified $L_\infty$ with factor $\beta_{\psi}$.

@@

$\hg$ is also a contraction map in the modified $L_\infty$ norm.

@@

Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\argmin_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then

@@

Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\infty,1/\psi}$ be the error due to ALUB projection and let $r^*\stackrel{\Delta}{=}\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\infty,1/\psi}$, then

@@

\textbf{Main Result~$1$: Prediction Error bound in modified $L_\infty$-norm}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Improved Bounds}\label{sec:improv}
In this section, we present improved error bounds by making use of Lyapunov functions. 
\begin{lemma}\label{bestbndmn}
Let $r^*\in \R^k$ be defined as $r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
\begin{align}
||J^*-\bj||_{\infty,1/\psi}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\infty,1/\psi} \psi\geq TJ^*$.
\end{proof}

Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the weighted $L_\infty$ norm.

@@

The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in weighted $L_\infty$ with factor $\beta_{\psi}$.

@@

$\hg$ is also a contraction map in the weighted $L_\infty$ norm.

@@

Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\eqdef\argmin_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then

@@

Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\infty,1/\psi}$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\infty,1/\psi}$, then

@@

\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}

### 2015-06-10 mdp.tex
eqdef and other minor fixes

%!TEX root =  autocontgrlp.tex
\section{Markov Decision Processes (MDPs)}
In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
An MDP is a $4$-tuple $\langle S,A,P,g\rangle$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g$ is the reward function. We consider MDPs with large but finite number of states. We also assume that the number of actions is finite.
Without the loss of generality, we set  $S=\{1,2,\ldots,n\}$  and the action set is given by $A=\{1,2,\ldots,d\}$. For simplicity, we assume that all actions are feasible in all states. 
The probability transition kernel $P= (p_a)_{a\in A}$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$. We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
By a policy, we mean a sequence $\pi=\{\pi_0,\ldots,\pi_n,\ldots\}$ of functions $\pi_n, n\geq 0$ 
	that describe the manner in which an action is picked in a given state at time $n$. 
In the most general case, $\pi_n$ maps $(S \times A)^n \times S$, i.e., 
	histories $h_n =(s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$ 
	of state-action sequences of length $2n+1$, to a distribution over the actions. 
We denote the class of policies by $\Pi$. 
The infinite horizon discounted reward corresponding to state $s$ under a policy $\pi$ is denoted by $J_\pi(s)$ and is defined by
\begin{align}
J_\pi(s)\stackrel{\Delta}{=}\E\left[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)\,\Large|\,\pi\right]\,,\nn
\end{align}
	where $a_{n} \sim \pi_n(\,\cdot\,|s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$, $s_{n+1} \sim p_{a_n}(s_n,\cdot)$ 
	and $\alpha \in (0,1)$ is a given discount factor. 
Here $J_\pi(s)$ is known as the value of the state $s$ under the policy $\pi$, and $J_\pi:S\to \R$ is 
 %the vector quantity $J_\pi\stackrel{\Delta}{=}(J_\pi(s))_{s\in S}\in R^n$ is 
 called the value-function corresponding to the policy $\pi$. 
 The optimal value function $J^*:S\to \R$ is defined as $J^*(s)\stackrel{def}{=}\underset{\pi \in \Pi}{\max} J_\pi(s)$, $s\in S$.

@@

Given an MDP, our aim is to find the optimal value function $J^*$ and an optimal policy SDP $u^*$. 
Any optimal policy $u^*$ and the value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
\begin{subequations}\label{bell}
\begin{align}
\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
\label{bellpol}u^*(s)&\in \argmax_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
\end{align}
\end{subequations}
If $J^*$ is computed first, then $u^*$ can be obtained via \eqref{bellpol}. 
For convenience, in what follows we identify $\R^n$ with $\R^{S}$:
Any vector $J\in \R^n$ is viewed as a real-valued function over $S$ via $J(s) = J_s$ and vice versa.
The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
\begin{definition}
The Bellman operator $T: \R^n \to \R^n$ is defined by 
\begin{align}
(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big)\,,  \qquad s\in S\,,J\in \R^n\,.
\end{align}
\end{definition}
Similarly one can define the Bellman operator restricted to an SDP $u$ as follows:
\begin{definition}
The Bellman operator $T_u:\R^n \to \R^n$  restricted to an SDP $u$ is defined by
\begin{align}
(T_uJ)(s)=g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\,,  \qquad s\in S\,,J\in \R^n\,.
\end{align}
\end{definition}
Given $J \in \R^n$, $TJ$ is the `one-step' greedy value function. It is also useful to define the notion of a one-step greedy policy as below:
\begin{definition}
A policy $\tilde{u}$ is said to be greedy with respect to $\tilde{J}$ if
\begin{align}\label{subpol}
\tilde{u}(s)\in \underset{a \in A}{\argmax} \, \big(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')\big)\,.
\end{align}
\end{definition}
We also define the Bellman operator $H$ for action values  \cite{BertB}: 
\begin{definition}\label{bellactval}
Let $H: \R^n \to \R^{nd}$ be defined as follows: For $J\in \R^n$,
\begin{align}
HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd}, \text{ where}\nn\\
(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \qquad s\in S, a\in A.
\end{align}
\end{definition}
We now state without proof the most important properties of the Bellman operator. 
Though in these results, we make use of the Bellman operator $T$, the results also trivially hold for $T_u$ as well.

%\subsection{Properties of $T$}
\begin{lemma}\label{maxnorm}
$T$ is a $\max$-norm contraction operator with contraction factor $\alpha$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
\begin{align}
||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
\end{align}
\end{lemma}
\begin{lemma}\label{uniquesol} 
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{lemma}
For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
The Bellman operator $T$ exhibits two more important properties presented in the following lemmas (see \cite{BertB} for proofs):
\begin{lemma}\label{monotone}
$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
Further, if $J\in \R^n$ is such that $J\geq TJ$ then $J\geq J^*$.
\end{lemma}
\begin{lemma}\label{shift}
Given $J\in \R^n$, $t \in \R$ and $\mathbf{1} \in \R^n$, a vector with all entries $1$, we have
\begin{align}
T(J+t\mathbf{1})=TJ+\alpha t\mathbf{1}.
\end{align}
\end{lemma}
Note that Lemmas~\ref{maxnorm}--\ref{shift} also hold for the Bellman operator $H$ defined for the action values in Definition~\ref{bellactval}.\par
Solving an MDP involves handling two sub-problems namely the problem of \emph{control} and the problem of \emph{prediction}. The problem of \emph{control} deals with coming up with a good (and if possible an optimal) policy. Often, in order to solve the problem of \emph{control}, one needs to solve the problem of \emph{prediction}, which deals with computing the value function $J_u$ of the policy $u$. The fact that the two problems are related is reflected in the Bellman equation in \eqref{bell}, where $J^*$ from \eqref{bellval} is used in \eqref{bellpol} to obtain an optimal policy $u^*$. Thus, the Bellman equation is at the heart of the solution methods to MDPs. Any solution method to MDP is said to be complete only if it satisfactorily (with provable performance guarantees) addresses both the prediction and the control problems. 
\todoc{Why insist on prediction?}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Markov Decision Processes (MDPs)}
In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
An MDP is a $4$-tuple $\langle S,A,P,g\rangle$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g$ is the reward function. We consider MDPs with large but finite number of states. We also assume that the number of actions is finite.
Without the loss of generality, we set  $S=\{1,2,\ldots,n\}$  and the action set is given by $A=\{1,2,\ldots,d\}$. For simplicity, we assume that all actions are feasible in all states. 
The probability transition kernel $P= (p_a)_{a\in A}$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$. We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
By a policy, we mean a sequence $\pi=\{\pi_0,\ldots,\pi_n,\ldots\}$ of functions $\pi_n, n\geq 0$ 
	that describe the manner in which an action is picked in a given state at time $n$. 
In the most general case, $\pi_n$ maps $(S \times A)^n \times S$, i.e., 
	histories $h_n =(s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$ 
	of state-action sequences of length $2n+1$, to a distribution over the actions. 
We denote the class of policies by $\Pi$. 
The infinite horizon discounted reward corresponding to state $s$ under a policy $\pi$ is denoted by $J_\pi(s)$ and is defined by \todoc{Explain the meaning of $\eqdef$.}
\begin{align}
J_\pi(s) \eqdef
	\E\left[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)\,\Large|\,\pi\right]\,,\nn
\end{align}
	where $a_{n} \sim \pi_n(\,\cdot\,|s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$, $s_{n+1} \sim p_{a_n}(s_n,\cdot)$ 
	and $\alpha \in (0,1)$ is a given discount factor. 
Here $J_\pi(s)$ is known as the value of the state $s$ under the policy $\pi$, and $J_\pi:S\to \R$ is 
 %the vector quantity $J_\pi\eqdef(J_\pi(s))_{s\in S}\in R^n$ is 
 called the value-function corresponding to the policy $\pi$. 
 The optimal value function $J^*:S\to \R$ is defined as $J^*(s) \eqdef
 \sup_{\pi\in\Pi} J_\pi(s)$, $s\in S$.
 %\underset{\pi \in \Pi}{\sup}\, J_\pi(s)$, $s\in S$.

@@

Given an MDP, our aim is to find the optimal value function $J^*$ and an optimal policy SDP $u^*$. 
Any optimal policy $u^*$ and the value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
\begin{subequations}\label{bell}
\begin{align}
\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
\label{bellpol}u^*(s)&\in \argmax_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
\end{align}
\end{subequations}
If $J^*$ is computed first, then $u^*$ can be obtained via \eqref{bellpol}.

For convenience, in what follows we identify $\R^n$ with $\R^{S}$:
Any vector $J\in \R^n$ is viewed as a real-valued function over $S$ via $J(s) = J_s$ and vice versa.
We now define some operators acting on $\R^n$ (equivalently, on $\R^S$) that will be useful later.
The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
\begin{definition}
The Bellman operator $T: \R^n \to \R^n$ is defined by 
\begin{align}
(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big)\,,  \qquad s\in S\,,J\in \R^n\,.
\end{align}
\end{definition}
Similarly one can define the Bellman operator restricted to an SDP $u$ as follows:
\begin{definition}
The Bellman operator $T_u:\R^n \to \R^n$  restricted to an SDP $u$ is defined by
\begin{align}
(T_uJ)(s)=g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\,,  \qquad s\in S\,,J\in \R^n\,.
\end{align}
\end{definition}
Given $J \in \R^n$, $TJ$ is the `one-step' greedy value function. It is also useful to define the notion of a one-step greedy policy as below:
\begin{definition}
A policy $\tilde{u}$ is said to be greedy with respect to $\tilde{J}$ if
\begin{align}\label{subpol}
\tilde{u}(s)\in \underset{a \in A}{\argmax} \, \big(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')\big)\,.
\end{align}
\end{definition}
We also define the Bellman operator $H$ for action values  \cite{BertB}: 
\begin{definition}\label{bellactval}
Let $H: \R^n \to \R^{nd}$ be defined as follows: For $J\in \R^n$,
\begin{align}
HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd}, \text{ where}\nn\\
(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \qquad s\in S, a\in A.
\end{align}
\end{definition}
We now state without proof the most important properties of the Bellman operator. 
Though in these results, we make use of the Bellman operator $T$, the results also trivially hold for $T_u$ as well.

%\subsection{Properties of $T$}
\begin{lemma}\label{maxnorm}
$T$ is a $\max$-norm contraction operator with contraction factor $\alpha$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
\todoc{Introduce $\norm{\cdot}_{\infty}$. Should we have a notation/symbols section?}
\begin{align}
||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
\end{align}
\end{lemma}
\begin{lemma}\label{uniquesol} 
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{lemma}
For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
The Bellman operator $T$ exhibits two more important properties presented in the following lemmas (see \cite{BertB} for proofs):
\begin{lemma}\label{monotone}
$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
Further, if $J\in \R^n$ is such that $J\geq TJ$ then $J\geq J^*$.
\end{lemma}
\begin{lemma}\label{shift}
Given $J\in \R^n$, $t \in \R$ and $\mathbf{1} \in \R^n$, a vector with all entries $1$, we have
\begin{align}
T(J+t\mathbf{1})=TJ+\alpha t\mathbf{1}.
\end{align}
\end{lemma}
Note that Lemmas~\ref{maxnorm}--\ref{shift} also hold for the Bellman operator $H$ defined for the action values in Definition~\ref{bellactval}.\par
Solving an MDP involves handling two sub-problems namely the problem of \emph{control} and the problem of \emph{prediction}. The problem of \emph{control} deals with coming up with a good (and if possible an optimal) policy. Often, in order to solve the problem of \emph{control}, one needs to solve the problem of \emph{prediction}, which deals with computing the value function $J_u$ of the policy $u$. The fact that the two problems are related is reflected in the Bellman equation in \eqref{bell}, where $J^*$ from \eqref{bellval} is used in \eqref{bellpol} to obtain an optimal policy $u^*$. Thus, the Bellman equation is at the heart of the solution methods to MDPs. Any solution method to MDP is said to be complete only if it satisfactorily (with provable performance guarantees) addresses both the prediction and the control problems. 
\todoc{Why insist on prediction?}

### 2015-06-10 strel.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4
address some comments
eqdef and other minor fixes

%!TEX root =  autocontgrlp.tex
\section{A simple bound}
The following lemmas relate the fixed point $\hv$ of $\hg$ to the solution $\hj$ of the GRLP in \eqref{grlp}.
\begin{lemma}\label{srw}
$\hat{r} \in \R^k$ is a solution to GRLP in \eqref{grlp} iff it solves the following program:
\begin{align}\label{grlpeqprog}
\min_{r\in \chi} &||\Phi r-\hv||_{1,c}\nn\\
\text{s.t}\mb & W^\top \Phi r\geq W^\top T \Phi r.
\end{align}
\end{lemma}
\begin{proof}
We know from Lemma~\ref{relation2} that $\hj\geq\hv$, and thus minimizing 
\begin{align*}
||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv
\end{align*} 
is the same as minimizing $c^\top \Phi r$.
\end{proof}
\begin{theorem}\label{mt2}
Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_\infty$ be the error due to ALUB projection and let $r^*\stackrel{\Delta}{=}\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_\infty$, then
\begin{align}
||\hj-\hv||_{1,c}\leq\frac{4||J^*-\Phi r^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_\infty$, then  it is easy to see that
\begin{align}
||J^*-T\Phi r^*||_\infty&=||TJ^*-T\Phi r^*||_\infty\leq\alpha\gamma,\mb\text{and}\nn\\
||T\Phi r^*-\Phi r^*||_\infty&\leq(1+\alpha)\gamma.
\end{align}
From Assumption~\ref{one} there exists $r'\in \R^k$ such that $\Phi r'=\Phi r^*+\frac{(1+\alpha)\gamma}{1-\alpha}\one$ and $r'$ is feasible to the ALP. \todoc{Why not just state that let $r' = r^* + \frac{(1+\alpha)\gamma}{1-\alpha} e_1$?}
Now
\begin{align}
||\Phi r'-J^*||_\infty&\leq ||\Phi r^* -J^*||_\infty+||\Phi r'-\Phi r^*||_\infty\nn\\&\leq \gamma+\frac{(1+\alpha)\gamma}{1-\alpha}=\frac{2\gamma}{1-\alpha}.
\label{mt2eq1}
\end{align}
Since $r'$ is also feasible for GRLP in \eqref{grlp} we have
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn &(\text{thanks to Lemma~\ref{srw}}) \\ %\vspace{10pt}
&\leq||\Phi r'-\hv||_\infty\mb & (\text{since $c$ is a distribution})\nn\\
&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty\,.\nn
\end{align}
The result follows from \eqref{mt2eq1} and Corollary~\ref{cmt1}.
\end{proof}\\
\textbf{Prediction Error bound in the $L_\infty$-norm}\\
\begin{corollary}\label{cmt2}
Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2}, then \todoc{Where is the effect of $\chi$?}
\begin{align}\label{finalbnd}
||J^*-\hj||_{1,c}\leq\frac{6 ||J^*-\Phi r^*||_\infty+2||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{corollary}
\begin{proof}
\begin{align}
||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq||J^*-\hv||_\infty+||\hv-\hj||_{1,c}\nn
\end{align}
The result now follows from Corollary~\ref{cmt1} and Theorem~\ref{mt2}.
\end{proof}
The results presented in Corollary~\ref{cmt2} is in the $L_\infty$-norm. In the next section, we use of Lyapunov functions to provide an improved bound in a modified $L_\infty$-norm.

>>>>

%!TEX root =  autocontgrlp.tex
\section{A simple bound}
The following lemmas relate the fixed point $\hv$ of $\hg$ to the solution $\hj$ of the GRLP in \eqref{grlp}.
\begin{lemma}\label{srw}
$\hat{r} \in \R^k$ is a solution to GRLP in \eqref{grlp} iff it solves the following program:
\begin{align}\label{grlpeqprog}
\begin{split}
\min_{r\in \chi}\, &||\Phi r-\hv||_{1,c}\\
\text{s.t}\mb & W^\top \Phi r\geq W^\top T \Phi r.
\end{split}
\end{align}
\end{lemma}
\begin{proof}
We know from Lemma~\ref{relation2} that $\hj\geq\hv$, and thus minimizing 
\begin{align*}
||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv
\end{align*} 
is the same as minimizing $c^\top \Phi r$.
\end{proof}
\begin{theorem}\label{mt2}
Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_\infty$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_\infty$, then
\begin{align}
||\hj-\hv||_{1,c}\leq\frac{4||J^*-\Phi r^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_\infty$, then  it is easy to see that
\begin{align}
||J^*-T\Phi r^*||_\infty&=||TJ^*-T\Phi r^*||_\infty\leq\alpha\gamma,\mb\text{and}\nn\\
||T\Phi r^*-\Phi r^*||_\infty&\leq(1+\alpha)\gamma.
\end{align}
From Assumption~\ref{one} there exists $r'= r^*+\frac{(1+\alpha)\gamma}{1-\alpha}\one$ and $r'$ is feasible to the ALP. \todoc{Why not just state that let $r' = r^* + \frac{(1+\alpha)\gamma}{1-\alpha} e_1$?}
Now
\begin{align}
||\Phi r'-J^*||_\infty&\leq ||\Phi r^* -J^*||_\infty+||\Phi r'-\Phi r^*||_\infty\nn\\&\leq \gamma+\frac{(1+\alpha)\gamma}{1-\alpha}=\frac{2\gamma}{1-\alpha}.
\label{mt2eq1}
\end{align}
Since $r'$ is also feasible for GRLP in \eqref{grlp} we have
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn &(\text{thanks to Lemma~\ref{srw}}) \\ %\vspace{10pt}
&\leq||\Phi r'-\hv||_\infty\mb & (\text{since $c$ is a distribution})\nn\\
&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty\,.\nn
\end{align}
The result follows from \eqref{mt2eq1} and Corollary~\ref{cmt1}.
\end{proof}\\
\textbf{Prediction Error bound in the $L_\infty$-norm}\\
\begin{corollary}\label{cmt2}
Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2}, then \todoc{Where is the effect of $\chi$?}
\begin{align}\label{finalbnd}
||J^*-\hj||_{1,c}\leq\frac{6 ||J^*-\Phi r^*||_\infty+2||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{corollary}
\begin{proof}
\begin{align}
||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq||J^*-\hv||_\infty+||\hv-\hj||_{1,c}\nn
\end{align}
The result now follows from Corollary~\ref{cmt1} and Theorem~\ref{mt2}.
\end{proof}
The results presented in Corollary~\ref{cmt2} is in the $L_\infty$-norm. In the next section, we use of Lyapunov functions to provide an improved bound in a modified $L_\infty$-norm.
